### 2015-05-13 related.tex
Addressed comments at the start of III

>>>>

Our pairwise approach to analysing driver entry points, employing abstraction to model additional threads, was inspired by the \emph{two thread reduction} used by the GPUVerify tool in the analysis of data-parallel OpenCL and CUDA kernels~\cite{gpuverify,bardsley2014engineering}.  The idea of pairwise analysis of components in a concurrent system has been broadly applied, notably in model checking of cache coherence protocols~\cite{mcmillan1999verification}.
